Targeted interrogation of mutational hotspots in rheumatoid arthritis

### 2024-03-11 infercnv/reports/gains_and_losses.Rmd
add uphyloplot repo

We also can observe the rate coincidence of chr7 and other gains. The LCM-WES data suggested a nested relationship in which there were chr5+ subclones within chr7+ populations. We look for this here.

@@

We also can run a Fisher exact test to test whether chr7+ and chr5+ gains co-occur more often than would be expected by chance, and also test all other co-occurences.

@@

@@

fisher %>%
  knitr::kable()
```

>>>>

### Co-occurence of CNV events

We also can observe the rate co-occurence of chr7+ and other CNVs. The LCM-WES data suggested a nested relationship in which there were chr5+ subclones within chr7+ populations. We look for this here.

@@

Here is a contingency table of the frequency of chr7+ versus chr5+ within cells.

@@

We can run a Fisher exact test to test whether chr7+ and chr5+ gains co-occur more often than would be expected by chance, and also test all other co-occurent CNV relationships.

@@

fisher %>%
  dplyr::mutate(p = format(p, digits = 3)) %>%
  knitr::kable()
```

### 2024-03-11 scomatic/reports/targeted_mutation_calling.Rmd
add uphyloplot repo

# recursites (to add detected mut)
recurmuts <-
  readr::read_tsv('recursites.tsv') %>%
  dplyr::transmute(
    chr,
    mut_pos = pos,
    mut_pos_lab = paste0(pos, '\ mut: ', mut)
  )

@@

>>>>

# recursites (to add detected mut)
recursites <-
  readr::read_tsv('recursites.tsv') 
recurmuts <-
  recursites %>%
  dplyr::transmute(
    chr,
    mut_pos = pos,
    mut_pos_lab = paste0(pos, '\ mut: ', mut)
  )

@@

## Recurrent mutations sites

Recurrent mutations from the LCM-WES data were found using `dNdScv`. Mutated sites in the following genes will be interrogated.

```{r plot_recurmuts, fig.width = 10}
recursites %>%
  dplyr::group_by(gene) %>%
  dplyr::mutate(sum_freq = sum(freq)) %>%
  ggplot(aes(x = reorder(gene, -sum_freq), y = freq, fill = qval)) +
  geom_col(position = 'stack') +
  scale_x_discrete(guide = guide_axis(angle = -90)) +
  labs(x = 'gene') +
  theme_classic()
```
